Emitter Source Geolocation from Imparted Rotor Blade Modulation

### 2016-10-11 Simulation.tex
update files

\chapter{Received Signal Simulations}
%define the signal characteristics and evaluate the properties of the resulting signal over the parameter sweeps

@@

After the computation of the short time Fourier transform the doppler envelope is calculated by performing a threshold on the power, in both the positive and negative doppler, at each time slice. The envelope value for that time slice is found by approaching zero frequency and stopping as the power reaches a predetermined level from both the negative and positive values. The power level to set the threshold is calculated differently based on weather the elevation or the azimuth parameter is being swept. For the azimuth angle sweep, which will be shown later in (-), the maximum power is found in each time slice then those values are averaged. Then for each successive angle the same average is taken and averaged with all the others

@@

This technique is used because the elevation angle is remaining constant, so the distance with the helicopter platform should be constant as well. When varying the elevation angle the same method cannot be used because the distance is changing so only the maximum power is found in each time slice then those values are averaged without any successive averaging.

@@

The effect of azimuth angle on the maximum measured doppler will be characterized in section (-)

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{Transmitter Elevation Angle}
%display elevation angle with respect to max doppler readings and describe patterns
The transmitter elevation angle is the angle between the helicopter rotor and the position of the transmitter shown in figure \ref{fig:azimuth_rel}.

@@

The effect of elevation angle on the maximum measured doppler will be characterized in section (-).

>>>>

\chapter{Received Signal Simulations} \label{ch:simulations}
%define the signal characteristics and evaluate the properties of the resulting signal over the parameter sweeps

@@

After the computation of the short time Fourier transform the doppler envelope is calculated by performing a threshold on the power, in both the positive and negative doppler, at each time slice. The envelope value for that time slice is found by approaching zero frequency and stopping as the power reaches a predetermined level from both the negative and positive values. The power level to set the threshold is calculated differently based on weather the elevation or the azimuth parameter is being swept. For the azimuth angle sweep, which will be shown later in section \ref{taa}, the maximum power is found in each time slice then those values are averaged. Then for each successive angle the same average is taken and averaged with all the others

@@

This technique is used because the elevation angle is remaining constant, so the distance with the helicopter platform should be constant as well. When varying the elevation angle in section \ref{sec:tea} the same method cannot be used because the distance is changing so only the maximum power is found in each time slice then those values are averaged without any successive averaging.

@@

The effect of pitching the blade is that it modifies the results of the azimuth sweep when compared to figure \ref{fig:tx_azimuth_angle_200}. The resulting min and max envelope frequencies vs azimuth angle for pitch are shown in \ref{fig:pitch_azimuth_rev}. This occurs because the pitch of the blade angles RF reflections more in the direction of travel but not at all points in the azimuth. When the transmitter is located between 90\textdegree and 270\textdegree pitch causes an increase in doppler but elsewhere decreases the amount of doppler shift. The decrease is caused by the blade surface top reflecting receding doppler away from the receiver at those angles.

%azimuth pitch effect
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/pitch_azimuth_rev.eps}
		\caption{Max and Min Envelope Frequencies vs Transmitter Elevation Angle with 7.5deg Pitch}
		\label{fig:pitch_azimuth_rev}
	\end{center}
\end{figure}

The effect of azimuth angle on the maximum measured doppler will be characterized in section \ref{sec:transmitter_azimuth_angle_estimation}

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{Transmitter Elevation Angle} \label{sec:tea}
%display elevation angle with respect to max doppler readings and describe patterns
The transmitter elevation angle is the angle between the helicopter rotor and the position of the transmitter shown in figure \ref{fig:azimuth_rel}.

@@

The effect of elevation angle on the maximum measured doppler will be characterized in section \ref{sec:transmitter_elevation_angle_estimation}.
